greta.Rmd

### 2019-08-12 notebook/may-outbreak-ghost.Rmd
saveRDS

states <- seq(0,2, length=200)
actions <- states
observations <- states
sigma_g <- 0.05
sigma_m <- 0.0

@@

```{r}
possible_a <- seq(.25, .34, by = 0.005)
true_a <- 0.27   ## reality has just a transient.  use  0.277 for stronger ghost
believe_a <- 0.29 ## believe there's an attractor
true_i <- which.min(abs(possible_a - true_a))
```

@@

```{r}
sim <- mdp_learning(transition, reward, discount, 
                    x0 = x0, 
                    Tmax = Tmax, 
                    true_transition = transition[[true_i]],
                    model_prior = prior,
                    type = "value iteration", 
                    epsilon = 1e-2)
```

@@

```{r}
```

>>>>

states <- seq(0,2, length=140)
actions <- states
observations <- states
sigma_g <- 0.05
sigma_m <- 0.0

@@

```{r}
possible_a <- seq(.25, .34, by = 0.005)
true_a <- 0.27   ## reality has just a transient.  use  0.277 for stronger ghost
believe_a <- 0.295 ## believe there's an attractor
true_i <- which.min(abs(possible_a - true_a))
```

@@

```{r}
set.seed(12345)
sim <- mdp_learning(transition, reward, discount, 
                    x0 = x0, 
                    Tmax = Tmax, 
                    true_transition = transition[[true_i]],
                    model_prior = prior,
                    type = "value iteration", 
                    epsilon = 1e-2)
```

@@

```{r}
saveRDS(sim, "sim-ghost-learning.Rds")
```
